Word2vec learns effective distance of scientific co-affiliation

### 2020-01-31 paper/current/main.tex
basic .tex cleanup and structuring of results section
removed "we" para openings, simplified intro.

@@

@@

@@

%\begin{minipage}{\figwidth} 
%\includegraphics[width=\linewidth]{\figdir/img} 
%\end{minipage}

@@

>>>>

%
% Subsection: Embedding performance
%
\subsection*{Embedding performance}

@@

%
% Subsection: Applications
%
\subsection*{Applications}
% Here we will examine several applications of this effective distnace, including for clustering, visualization + descriptive analysis, and maybe something else?

@@

%
% Subsection: Mathematical Exploration
%
\subsection*{Mathematical Exploration}

@@

@@

%
% Figure - publications over time
%
\begin{figure}[p!]
	\centering
	\label{fig:supp:pubs_over_time}
	\includegraphics[width=\textwidth]{\figdir/Descriptive/mobility_by_country.pdf}
	\caption{
		\textbf{Extend and nature of mobility by country.}
		\textbf{a.}
		Proportion of researchers in each country classified as mobile, meaning that they have at least two organization affiliations within the period of study. 
		The countires with the most mobile researchers are the United States, China, France, Great Britain, and Germany. 
		\textbf{b.}
		The same information, arranged into a cumulative distribution.
		The five countires with the highest mobility account for a total of 
	}
\end{figure}
